
% \bibliographystyle{plain}
%\bibliographystyle{GBT7714-2005NLang_Upp}
%\bibliography{references}
%& This .bbl file has been processed by fixbbl!
%& This .bbl file has been processed by fixbbl!
\begin{thebibliography}{148}
\addtolength{\itemsep}{-1.5em}
\setlength{\itemsep}{-1.0pt}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
\providecommand{\doi}[1]{doi: #1}\else
\providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem{avitrack}
Lipton A J, Fujiyoshi H, Patil R S. Moving Target Classification and Tracking from Real-time Video[C]// IEEE Workshop on Applications of Computer Vision. IEEE Computer Society, 1998:129--136.
\bibitem{vehicle}
Ashton S J, Mackay G M. Benefits from Changes in Vehicle Exterior Design – Field Accident and Experimental Work in Europe[J]. Publication of Society of Automotive Engineers Incorporated, 1983:255-263.
\bibitem{tld}
Kalal Z, Mikolajczyk K, Matas J. Tracking-Learning-Detection.[J]. IEEE Transactions on Pattern Analysis and Machine Intelligence, 2012, 34(7):1409-1422.
\bibitem{viola-jones}
Viola P, Jones M. Rapid object detection using a boosted cascade of simple features[C]. Computer Vision and Pattern Recognition, 2001. CVPR 2001. Proceedings of the 2001 IEEE Computer Society Conference on. IEEE, 2001, 1: I-511-I-518 vol. 1.
\bibitem{via-jones-face}
Viola P, Jones M J. Robust real-time face detection[J]. International journal of computer vision, 2004, 57(2): 137-154.
\bibitem{hog}
Dalal N, Triggs B. Histograms of oriented gradients for human detection[C]//2005 IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR'05). IEEE, 2005, 1: 886-893.
\bibitem{dpm}
Felzenszwalb P F, Girshick R B, McAllester D, et al. Object detection with discriminatively trained part-based models[J]. IEEE transactions on pattern analysis and machine intelligence, 2010, 32(9): 1627-1645.
\bibitem{ensemble}
Barron J L, Fleet D J, Beauchemin S S, et al. Performance of optical flow techniques[J]. International Journal of Computer Vision, 1994, 12(1):43-77.
\bibitem{ren}
徐小明. 摄像机运动条件下动目标检测方法研究[D]. 南昌航空大学, 2011.
\bibitem{wang}
郑世友. 动态场景图像序列中运动目标检测与跟踪[D]. 东南大学, 2006.
\bibitem{alexnet}
Krizhevsky A, Sutskever I, Hinton G E. Imagenet classification with deep convolutional neural networks[C]//Advances in neural information processing systems. 2012: 1097-1105.
\bibitem{multibox}
Szegedy C, Reed S, Erhan D, et al. Scalable, High-Quality Object Detection[J]. Computer Science, 2015.
\bibitem{overfeat}
Sermanet P, Eigen D, Zhang X, et al. OverFeat: Integrated Recognition, Localization and Detection using Convolutional Networks[J]. Eprint Arxiv, 2014.
\bibitem{rcnn}
Girshick R, Donahue J, Darrell T, et al. Rich feature hierarchies for accurate object detection and semantic segmentation[C]//Proceedings of the IEEE conference on computer vision and pattern recognition. 2014: 580-587.
\bibitem{vgg}
Simonyan K, Zisserman A. Very deep convolutional networks for large-scale image recognition[J]. arXiv preprint arXiv:1409.1556, 2014.
\bibitem{sppnet}
He K, Zhang X, Ren S, et al. Spatial pyramid pooling in deep convolutional networks for visual recognition[C]//European Conference on Computer Vision. Springer International Publishing, 2014: 346-361.
\bibitem{fast-rcnn}
Girshick R. Fast r-cnn[C]//Proceedings of the IEEE International Conference on Computer Vision. 2015: 1440-1448.
\bibitem{faster rcnn}
Ren S, He K, Girshick R, et al. Faster R-CNN: Towards real-time object detection with region proposal networks[C]//Advances in neural information processing systems. 2015: 91-99.
\bibitem{keypoint}
Arnaud E, Fauvet B, Memin E, et al. A robust and automatic face tracker dedicated to broadcast videos[C]// IEEE International Conference on Image Processing. 2005:III - 429-32.
\bibitem{harris}
Birchfield S T, Rangarajan S. Spatiograms versus Histograms for Region-Based Tracking[C]// IEEE Computer Society Conference on Computer Vision and Pattern Recognition. 2005:1158-1163.
\bibitem{klt}
Laganiere R, Gilbert S, Roth G. Robust Object Pose Estimation From Feature-Based Stereo[J]. IEEE Transactions on Instrumentation and Measurement, 2006, 55(4):1270 - 1280.
\bibitem{correlation}
Chalidabhongse T H, Kim K, Harwood D, et al. A perturbation method for evaluating background subtraction algorithms[J]. Joint IEEE International Workshop on Visual Surveillance and Performance Evaluation of Tracking and Surveillance (VS-PETS, 2009.
\bibitem{error}
Gao X, Boult T E, Coetzee F, et al. Error Analysis of Background Adaption[C]// 2000 Conference on Computer Vision and Pattern Recognition (CVPR 2000), 13-15 June 2000, Hilton Head, SC, USA. 2000:1503-1510.
\bibitem{lbp}
Ojala T, Pietikainen M, Harwood D. Performance evaluation of texture measures with classification based on Kullback discrimination of distributions[C]//Pattern Recognition, 1994. Vol. 1-Conference A: Computer Vision \&amp; Image Processing., Proceedings of the 12th IAPR International Conference on. IEEE, 1994, 1: 582-585.
\bibitem{selective-search}
Uijlings J R R, van de Sande K E A, Gevers T, et al. Selective search for object recognition[J]. International journal of computer vision, 2013, 104(2): 154-171.
\bibitem{edge-box}
Zitnick C L, Dollár P. Edge boxes: Locating object proposals from edges[C]//European Conference on Computer Vision. Springer International Publishing, 2014: 391-405.
\bibitem{mcg}
Arbeláez P, Pont-Tuset J, Barron J T, et al. Multiscale combinatorial grouping[C]//Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2014: 328-335.
\bibitem{resnet}
He K, Zhang X, Ren S, et al. Deep residual learning for image recognition[J]. arXiv preprint arXiv:1512.03385, 2015.
\bibitem{inception-v4}
Szegedy C, Ioffe S, Vanhoucke V. Inception-v4, inception-resnet and the impact of residual connections on learning[J]. arXiv preprint arXiv:1602.07261, 2016.
\bibitem{pascal-voc-2010}
Everingham M, Van~Gool L, Williams C~K~I, et al. The {PASCAL} {V}isual {O}bject {C}lasses {C}hallenge 2010 {(VOC2010)}
{R}esults. \url{http://www.pascal-network.org/challenges/VOC/voc2010/workshop/index.html}.
\bibitem{cifar-10}
Krizhevsky A, Hinton G. Learning multiple layers of features from tiny images[J]. 2009.
\bibitem{mnist}
LeCun Y, Bottou L, Bengio Y, et al. Gradient-based learning applied to document recognition[J]. Proceedings of the IEEE, 1998, 86(11): 2278-2324.
\bibitem{relu}
Nair V, Hinton G E. Rectified linear units improve restricted boltzmann machines[C]//Proceedings of the 27th International Conference on Machine Learning (ICML-10). 2010: 807-814.
\bibitem{parsenet}
Liu W, Rabinovich A, Berg A C. Parsenet: Looking wider to see better[J]. arXiv preprint arXiv:1506.04579, 2015.
\bibitem{zfnet}
Zeiler M D, Fergus R. Visualizing and understanding convolutional networks[C]//European Conference on Computer Vision. Springer International Publishing, 2014: 818-833.

\bibitem{imagenet}
Russakovsky O, Deng J, Su H, et al. Imagenet large scale visual recognition challenge[J]. International Journal of Computer Vision, 2015, 115(3): 211-252.
\bibitem{coco}
Lin T Y, Maire M, Belongie S, et al. Microsoft coco: Common objects in context[C]//European Conference on Computer Vision. Springer International Publishing, 2014: 740-755.
\bibitem{yolo}
Redmon J, Divvala S, Girshick R, et al. You only look once: Unified, real-time object detection[J]. arXiv preprint arXiv:1506.02640, 2015.
\bibitem{ssd}
Liu W, Anguelov D, Erhan D, et al. SSD: Single Shot MultiBox Detector[J]. arXiv preprint arXiv:1512.02325, 2015.
\bibitem{pascal-voc-2007}
Everingham M, Van~Gool L, Williams C~K~I, et al. The {PASCAL} {V}isual {O}bject {C}lasses {C}hallenge 2007 {(VOC2007)}
{R}esults. \url{http://www.pascal-network.org/challenges/VOC/voc2007/workshop/index.html}.
\bibitem{mscnn}
Cai Z, Fan Q, Feris R S, et al. A unified multi-scale deep convolutional neural network for fast object detection[C]//European Conference on Computer Vision. Springer International Publishing, 2016: 354-370.
\bibitem{atrous}
Holschneider M, Kronland-Martinet R, Morlet J, et al. A real-time algorithm for signal analysis with the help of the wavelet transform[M]//Wavelets. Springer Berlin Heidelberg, 1990: 286-297.
\bibitem{deeplab}
Chen L C, Papandreou G, Kokkinos I, et al. Semantic image segmentation with deep convolutional nets and fully connected crfs[J]. arXiv preprint arXiv:1412.7062, 2014.
\bibitem{proposal}
Hosang J, Benenson R, Dollár P, et al. What makes for effective detection proposals?[J]. IEEE transactions on pattern analysis and machine intelligence, 2016, 38(4): 814-830.
\bibitem{sdp}
Yang F, Choi W, Lin Y. Exploit all the layers: Fast and accurate cnn object detector with scale dependent pooling and cascaded rejection classifiers[C]//Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2016: 2129-2137.
\bibitem{segnet}
Badrinarayanan V, Handa A, Cipolla R. Segnet: A deep convolutional encoder-decoder architecture for robust semantic pixel-wise labelling[J]. arXiv preprint arXiv:1505.07293, 2015.
\bibitem{fcn}
Long J, Shelhamer E, Darrell T. Fully convolutional networks for semantic segmentation[C]//Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2015: 3431-3440.
\bibitem{struck}
Hare S, Saffari A, Torr P H S. Struck: Structured output tracking with kernels[C]// International Conference on Computer Vision. IEEE Trans Pattern Anal Mach Intell, 2011:263-270.
\bibitem{kcf}
Henriques J F, Caseiro R, Martins P, et al. High-Speed Tracking with Kernelized Correlation Filters[J]. IEEE Transactions on Pattern Analysis and Machine Intelligence, 2015, 37(3):583-596.
\bibitem{p-n}
Kalal Z, Matas J, Mikolajczyk K. P-N learning: Bootstrapping binary classifiers by structural constraints[J]. 2010, 238(6):49-56.
\bibitem{rank-svm}
Bai Y, Tang M. Robust tracking via weakly supervised ranking svm[C]//Computer Vision and Pattern Recognition (CVPR), 2012 IEEE Conference on. IEEE, 2012: 1854-1861.
\bibitem{boost-track}
Grabner H, Leistner C, Bischof H. Semi-supervised on-line boosting for robust tracking[C]//European conference on computer vision. Springer Berlin Heidelberg, 2008: 234-247.
\bibitem{multi-view}
Saffari A, Leistner C, Godec M, et al. Robust multi-view boosting with priors[C]//European Conference on Computer Vision. Springer Berlin Heidelberg, 2010: 776-789.
\bibitem{mil}
Babenko B, Yang M H, Belongie S. Visual tracking with online multiple instance learning[C]//Computer Vision and Pattern Recognition, 2009. CVPR 2009. IEEE Conference on. IEEE, 2009: 983-990.
\bibitem{mib}
Zeisl B, Leistner C, Saffari A, et al. On-line semi-supervised multiple-instance boosting[C]//Computer Vision and Pattern Recognition (CVPR), 2010 IEEE Conference on. IEEE, 2010: 1879-1879.
\bibitem{ohem}
Shrivastava A, Gupta A, Girshick R. Training region-based object detectors with online hard example mining[J]. arXiv preprint arXiv:1604.03540, 2016.
\bibitem{densebox}
Huang L, Yang Y, Deng Y, et al. Densebox: Unifying landmark localization with end to end object detection[J]. arXiv preprint arXiv:1509.04874, 2015.
\bibitem{batch-norm}
Ioffe S, Szegedy C. Batch normalization: Accelerating deep network training by reducing internal covariate shift[J]. arXiv preprint arXiv:1502.03167, 2015.
\bibitem{larank}
Bordes A, Bottou L, Gallinari P, et al. Solving multiclass support vector machines with LaRank[C]//Proceedings of the 24th international conference on Machine learning. ACM, 2007: 89-96.
\bibitem{benchmark}
Wu Y, Lim J, Yang M H. Online object tracking: A benchmark[C]//Proceedings of the IEEE conference on computer vision and pattern recognition. 2013: 2411-2418.
\end{thebibliography}
